Formalisation of Session-based Lambda Calculus Type Systems

### 2014-11-14 proposal/proposal.tex
Finished review of piDILL paper.

So we have work on pi calculus and linear logic by \citeauthor{Caires:2010:STI}~\cite{Caires:2010:STI}.

@@

A number of systems incorporate both a functional language surface syntax with and translation to a more primitive process calculus. \citeauthor{Wadler:2012}'s recent work~\cite{Wadler:2012} fuses together a process calculus, CP, based on earlier work, on a relationship between the $\pi$ calculus and linear logic, by \citeauthor{Caires:2010:STI} with a functional language, GV, based on LAST by \citeauthor{Gay:2010:LAST}. The work describes a continuation-passing style (CPS) translation from GV to CP treating session types as propositions in a classical linear logic.

>>>>

\citeauthor{Caires:2010:STI} \cite{Caires:2010:STI} provide a $\pi$ calculus type system with session types.
They use a labelled transition system to represent process reduction with observable actions on channels.
The relationship with intuitionistic linear logic provides absence of deadlocks in session-based communication.
There is structural and congruence rules for processes.

@@

A number of systems incorporate both a functional language surface syntax with and translation to a more primitive process calculus. \citeauthor{Wadler:2012}'s recent work~\cite{Wadler:2012} fuses together a process calculus, CP, based on earlier work, on a relationship between the $\pi$ calculus and linear logic, by \citeauthor{Caires:2010:STI} with a functional language, GV, based on LAST by \citeauthor{Gay:2010:LAST}. The work describes a continuation-passing style (CPS) translation from GV to CP treating session types as propositions in a classical linear logic.
The process calculus is slightly different to that described in the $\pi$DILL apart from being classical in nature the constructs for server replication are different, CP provides a weakening and contraction semantics whereas this is encode in one rule for process reduction by caires
Wadler also dispenses with the structural rules; subsumed by the Assoc and Swap typing derivations and the cut reduction (double check why he does this)
